%Individual baryon number is violated by flavor proceases

%Total baryon number is accidentaly conseeved.

%U(1)_B is not requires to be local. In fact it needsto be global to allow for sphalwrons

% Lepton number can be a local symmetry

%Nice if it can explain something


The interpretation of neutrino experimental data in terms of neutrino oscillations  is compatible with both Majorana and Dirac neutrino masses. Regarding the last possibility,it is worth noticing that the lack of signals in the ongoing neutrinoless double beta decay experiments left  open the possibility of Dirac neutrinos.

%requires some symmetry


In such a case, the total Lepton number $L$ is a symmetry of nature.

%The new symmetey of nature
However, introducing a set of right handed neutrinos with with $L=-1$,
such that the Majorana terms are forbidden, requires too small Yukawa cuplings, of $\mathcal{O}(10^{-11})$. Much more smaller than the SM ones. In this way, an explanation of the smallness of the neutrino masses is still required. We assume here that the smallness of neutrino masses arise from a spotaneosly broken Abelian gauge symmetry responsible for the conservation of total number in nature. Therefore, we have the prediiction of relativistic degrees of freedom which can termalize in the early universe throgh interactions wih the new massive gauge bosons.

To explain the smallness of neutrino masses it is expected that they appear as a realization of at least a  dimension five operator. The only dimension five operator in the Standard Model (SM) violates total $L$  by two units and therefore is not suitable to explain the smallneaa of Dirac neutrino masses.

In this work we assune that total $L=L_e+L_\mu+L_\tau$ arise as the remnant of an Abelian symmetry, spontaneoualy broken by the vacuum expectation value (vev) of a singlet scalar $S$. % whose imaginay part is eaten up by a massive extra gauge boson.

In this extension of the standar model, the dimension five operator which conserves total Lepton number is~\cite{}
\begin{align}
  \mathcal{L}=
  \frac{h_{\alpha}}{\Lambda} (\nu_{R_\alpha})^\dagger \epsilon_{ab}L^a H^b S + \text{h.c}\,,
\end{align}
where $\nu_{R_\alpha}$ is the right-handed part of  the $\alpha$ neutrino Dirac fermion, $H$ is the SM higgs doublet with $1/2$ hypercharge,
$h_{\alpha}$ is an adimensional coupling, and $\Lambda$ is the scale of new physics.

We assume from now on that the charges under the new Abelian group forbids the tree level (TL) Lagrangian
\begin{align}
 \mathcal{L}= & h_{\nu_{\alpha i}}(\nu_{R_\alpha})^\dagger \epsilon_{ab}L^a_i H^b+M_{R_\alpha\beta}
  \nu_{R_\alpha} \nu_{R_\beta}+
  \text{h.c}\,.
\end{align}
In this way,  the tree level mass for both the Dirac and Majorana neutrinos are forbidden. In particular, this excludes the aolution with Lepton parity as a renmant symmetry, under which the right-handed neutrinos, $\nu_R$, and the standard model leptons have charge $-1$.

%note that have only two RH with -1 may allos for solurions with Dirac Fermion DM.

%Something about B-L fot allow minimal number of fields

Global with fermion dark matter imply colored DM
